Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-23 ms.tex
data section

% mention frequency range 100-3000 GHz ?
% cite the FDS99 model in the intro as well ?
% mention that this isn't just a Planck-based SED, but includes DIRBE/IRAS ?
% mention that this is first ever thermal dust model based on Planck 2015 ?

@@

>>>>

% cite the FDS99 model in the intro as well ?
% mention that this isn't just a Planck-based SED, but includes DIRBE/IRAS ?
% mention that this is first ever thermal dust model based on Planck 2015 ?

@@

The \PLANCK~frequency maps utilized throughout this work are drawn from the 
\PLANCK~2015 data release \citep{planck2015}. Specifically, we have made use 
of all six of the zodiacal light corrected HFI intensity maps
\citep[\texttt{2048\_R2.00\_full\_ZodiCorrected},][]{planckzodi}.

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the 
\citet[henceforth SFD]{SFD} reprocessing of DIRBE/\IRAS~100$\mu$m, which we 
will refer to as \verb|i100|, and at times by frequency as 3000 GHz. The 
\verb|i100| map has angular resolution of $6.1'$, and was constructed so as to 
contain only thermal emission from Galactic dust, with compact sources and 
zodiacal light removed, and its zero level tied to H\,\textsc{i}. We use the 
\verb|i100| map as is, without any custom modifications.

In some of our FIR dust SED analyses which do not require high angular 
resolution, specifically those of $\S$\ref{sec:global}, $\S$\ref{sec:lores}, 
and $\S$\ref{sec:hier}, we also make use of the SFD reprocessings of DIRBE 
140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz).
